upwell_IDX

### 2019-09-05 SST_patterns.Rmd
updated

# nc_data <- nc_open('/home/amieroh/Documents/Data/Datasets/MUR/daily/20020601-JPL-L4UHfnd-GLOB-v01-fv04-MUR.nc')
# print(nc_data)

ncDir <- "/home/amieroh/Documents/Data/Datasets/MUR/daily"
csvDir <- "/home/amieroh/Documents"

bbox <- data.frame(BC = c(-35, -25, 15, 20), # Benguela Current
                   CC = c(25, 35, 340, 355), # Canary Current
                   CalC = c(35, 45, 225, 240), # California Current
                   HC = c(-17.5, -7.5, 275, 290), # Humboldt Current
                   row.names = c("latmin", "latmax", "lonmin", "lonmax"))

@@

@@

@@

```{r}
ncDir <- "/home/amieroh/Documents/Data/Datasets/CMC/CMC_global"
csvDir <- "/home/amieroh/Documents"

bbox <- data.frame(BC = c(-35, -25, 15, 20), # Benguela Current
                    CC = c(25, 35, 340, 355), # Canary Current
                   CalC = c(35, 45, 225, 240), # California Current
                   HC = c(-17.5, -7.5, 275, 290), # Humboldt Current
                   row.names = c("latmin", "latmax", "lonmin", "lonmax"))

#          1         2         3         4
# 12345678901234567890123456789012345678901

read_nc <- function(ncFile = ncFile, region = region, csvDir = csvDir) {
  coords <- bbox[,region]
    nc <- nc_open(ncFile)
    pathLen <- nchar(paste0(ncDir, "/", region)) + 1
    fNameStem <-
      substr(ncFile, pathLen + 10, pathLen + 38)
    fDate <- substr(ncFile, pathLen + 1, pathLen + 8)
    sst <- ncvar_get(nc, varid = "analysed_sst") %>%
      round(4)
    dimnames(sst) <- list(lon = nc$dim$lon$vals,
                          lat = nc$dim$lat$vals)
    nc_close(nc)
    sst <-
      as.data.frame(melt(sst, value.name = "temp"), row.names = NULL) %>%
      mutate(t = ymd(fDate)) %>%
      na.omit()
    fwrite(sst,
           file = paste0(csvDir, "/", region, "-", fNameStem, "-", strtDate, "-", endDate, ".csv"),
           append = TRUE, col.names = FALSE)
    rm(sst)
}

# the list of files
ncList <- list.files(path = ncDir, pattern = "*.nc", full.names = TRUE, include.dirs = TRUE)
strtDate <- str_sub(ncList[1], start = 1, end = 8)
endDate <- str_sub(ncList[length(ncList)], start = 1, end = 8)

# apply the function
system.time(llply(ncList, read_nc, region = "BC", csvDir = csvDir, .parallel = TRUE))

ncDir <- "/Volumes/Challenger_Deep/OceanData/CMC0.2deg-CMC-L4-GLOB-v2.0/netCDF"
```

>>>>

print(nc_data)

ncDir <- "/home/amieroh/Documents/Data/Datasets/MUR/daily"
csvDir <- "/home/amieroh/Documents/Data/Datasets/MUR/Extracted_MUR"

@@

ncFile <- '/home/amieroh/Documents/Data/Datasets/MUR/daily/20020601-JPL-L4UHfnd-GLOB-v01-fv04-MUR.nc'

@@

llply(ncList, ncFun, csvDir = csvDir, .parallel = TRUE)

MUR <- read_csv("~/Documents/JPL-L4UHfnd-GLOB-v01-fv03-MUR-20020601-20140727.csv")
names(MUR)<-c("lon","lat", "temp", "date")
MUR <- MUR %>% 
  mutate(temp = temp - 273.15)

JPL_L4UHfnd_GLOB_v01_fv04_MUR_20020601_20140727 <- read_csv("~/Documents/JPL-L4UHfnd-GLOB-v01-fv04-MUR-20020601-20140727.csv")
```

```{r}
ncDir <- "/home/amieroh/Documents/Data/Datasets/CMC/CMC_BC"
csvDir <- "/home/amieroh/Documents"

#          1         2         3         4         5         6
# 123456789012345678901234567890123456789012345678901234567890
# 20100609-JPL_OUROCEAN-L4UHfnd-GLOB-v01-fv01_0-G1SST_subset.nc
read_nc <- function(ncDir = ncDir, csvDir = csvDir) 
  ncList <- list.files(path = paste0(ncDir), pattern = "*.nc", full.names = TRUE, include.dirs = TRUE)
  ncFirst <- head(list.files(path = paste0(ncDir, "/"), pattern = "*.nc", full.names = FALSE), 1)
  ncLast <- tail(list.files(path = paste0(ncDir, "/"), pattern = "*.nc", full.names = FALSE), 1)
  strtDate <- str_sub(ncFirst, start = 1, end = 8)
  endDate <- str_sub(ncLast, start = 1, end = 8)

# ncFile <- '/home/amieroh/Documents/Data/Datasets/CMC/CMC_BC/20100609-JPL_OUROCEAN-L4UHfnd-GLOB-v01-fv01_0-G1SST_subset.nc'

  ncFun <- function(ncFile = ncFile, csvDir = csvDir) {
    nc <- nc_open(ncFile)
    pathLen <- nchar(paste0(ncDir, "/")) + 1
    fNameStem <-
      substr(basename(ncFile), 10, 58)
    fDate <- substr(basename(ncFile), 1, 8)
    sst <- ncvar_get(nc, varid = "analysed_sst") %>%
      round(4)
    dimnames(sst) <- list(lon = nc$dim$lon$vals,
                          lat = nc$dim$lat$vals)
    nc_close(nc)
    sst <- as_tibble(melt(sst, value.name = "temp"))
    sst$t <- ymd(fDate)
    na.omit(sst)
    fwrite(sst,
           file = paste0(csvDir, "/", fNameStem, "-", strtDate, "-", endDate, ".csv"),
           append = TRUE, col.names = FALSE)
    rm(sst)
  }

@@

### 2019-09-05 upwell_IDX.Rmd
updated

  # Visualise
  world_map +
    geom_segment(data = site_list, colour = "red4", 
                 aes(x = lon, y = lat, xend = lon_dest, yend = lat_dest)) +
    geom_point(data = site_list, size = 3, colour = "black", aes(x = lon, y = lat)) +
    geom_point(data = site_list, size = 3, colour = "red", aes(x = lon_dest, y = lat_dest)) +
    coord_cartesian(xlim = c(min(site_list$lon - buffer), 
                             max(site_list$lon + buffer)),
                    ylim = c(min(site_list$lat - buffer), 
                             max(site_list$lat + buffer))) +
    labs(x = "", y = "", colour = "Site\norder") +
    ggtitle(titles[title_choice])
}
south_africa_away <- plot_sites(south_africa_away_wide, 1, 1, 100000)
```

@@

##################### Upwelling ######################
# Min duration for an upwelling event - 1day and threshold -1. Upwelling can over within a few hours, but given that we have daily data - upwelling has a minimum duration of 1 day
# Seasonal upwelling. Upwelling seasons are summer and spring
# Did the wind intensify? This is usually done by taking first third of the dataset and the last thid of the dataset and doing a t-test on this
# Strong south easterly winds lead to a stronger upwelling event
##############################################

>>>>

  # Visualise
  world_map +
    geom_segment(data = site_list, colour = "red4", 
                 aes(x = lon, y = lat, xend = lon_dest, yend = lat_dest)) +
    geom_point(data = site_list, size = 3, colour = "black", aes(x = lon, y = lat)) +
    geom_point(data = site_list, size = 3, colour = "red", aes(x = lon_dest, y = lat_dest)) +
    coord_cartesian(xlim = c(min(site_list$lon - buffer), 
                             max(site_list$lon + buffer)),
                    ylim = c(min(site_list$lat - buffer), 
                             max(site_list$lat + buffer))) +
    labs(x = "", y = "", colour = "Site\norder") +
    ggtitle(titles[title_choice])
}
south_africa_away <- plot_sites(south_africa_away_wide, 1, 1, 100000)
south_africa_away
```

@@

# Bits of code testing the thresholds against the upwelling literature
##################### Upwelling ######################
# Min duration for an upwelling event - 1day and threshold -1. Upwelling can over within a few hours, but given that we have daily data - upwelling has a minimum duration of 1 day
# Seasonal upwelling. Upwelling seasons are summer and spring
# Did the wind intensify? This is usually done by taking first third of the dataset and the last thid of the dataset and doing a t-test on this
# Strong south easterly winds lead to a stronger upwelling event
##############################################
